\subsubsection{Easy remote access}
All latest releases of HestiaPi offer very easy remote access to your home
without touching your network modem/router or even knowing HestiaPi's IP! Does
not depend on port forwarding or DynDNS! Woohooo!

\textbf{Please note that this is an externally hosted service not controlled by
you or us but by OpenHAB itself.}

\href{https://www.youtube.com/watch?v=joz5f4ejJVc}{Instructions video} (if you
prefer video to text)

To activate it (shipped disabled by default for obvious reasons) go to
http://[YOUR-HESTIAPI-IP]:8080/paperui/index.html and select Add-ons > MISC and make
sure ``openHAB Cloud Connector'' is installed.

Once installed SSH into your HestiaPi (username: pi and password: hestia) and
type:

\texttt{    cat /var/lib/openhab2/uuid}

 copy the output somewhere. Then type:

\texttt{        cat /var/lib/openhab2/openhabcloud/secret}

copy this output too. Reboot your HestiaPi

\texttt{        sudo reboot}

    
Then go to \url{https://myopenhab.org} and create an account using your details
and the above information (UUID and secret).

You can now access your HestiaPi Touch from a browser or your mobile app

Hint: Enter \url{https://myopenhab.org} as a remote url and your myopenHAB
account username and password as credentials

\subsubsection{Traditional remote access}

You will need a WiFi router with port forwarding feature (most routers do these
days) and if you don’t have a static IP (or if you don’t know what this is),
you will need to use a free Dynamic DNS service called
\href{https://www.noip.com/support/knowledgebase/install-ip-duc-onto-raspberry-pi/}{NoIP}.
Don’t worry -- although we can’t offer support on individual routers, we can
certainly point you in the right direction. Installation instructions on the
above link.  Alternatively you can use my.openhab.org which is a service hosted
externally and is not controlled by us or you but by OpenHAB itself. Go to:

\texttt{http://[YOUR-HESTIAPI-IP]:8080/paperui/index.html}

and select Add-ons > MISC and install ``openHAB Cloud Connector'' if not
installed. Once installed SSH into your HestiaPi (username: pi and password:
hestia) and type:

\texttt{cat /var/lib/openhab2/uuid}

write the output down. Then type:

\texttt{cat /var/lib/openhab2/openhabcloud/secret}

write this output down too.

Then go to \url{https://myopenhab.org} and create an account using your details
and the above information (UUID and secret). You can now access your HestiaPi
Touch from a browser or your mobile app (enter ``\url{https://myopenhab.org}''
as a remote url and your myopenHAB account username and password as
credentials).  The above steps are also available in youtube format
\href{https://www.youtube.com/watch?v=joz5f4ejJVc}{here} too.
